FITC analysis script - round 4

### 2022-11-13 code/Round 1/Cytokines adjusted.Rmd
Almost done with results

```{r load data and set tissue type, include=FALSE}
#set tissue type
sample_tissue <- "ileum"
study_round <- "2"
```

@@

#Density plots to show distribution of cytokines
histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = values, fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

@@

tbl1 <- cytokines %>% 
  filter(exp_number == "1") %>% 
  filter(tissue == sample_tissue) %>% 
  select(group,INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no",
              include = !"INFg",
             # statistic = list(all_continuous() ~ "{mean} ({sd})")  #Un-comment this line to get mean+sd. 
             #%>%
statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  add_p() %>% 
  #modify_footnote("Exp. 1") %>% 
  modify_header(
    label ~ "Cytokines") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3", "stat_4") ~ "Treatment groups (N total = {N})"))

  tbl1_gt <- tbl1 %>% 
  as_gt() %>%
  #tab_header(title = md("**Proinflammatory cytokines**")) %>%
  opt_align_table_header("center") %>% 
  # tab_options(heading.title.font.size = 20,
  #             heading.background.color = "lightgrey",
  #             ) %>% 
  tab_source_note(
    source_note = " * P-value indicates overall group differences"
  ) %>%
  tab_source_note(
    source_note = md("**Matrinem round 1**")
  ) %>%
  cols_width(label ~ px(100),
             stat_1 ~ px(150),
             stat_2 ~ px(150),
             stat_3 ~ px(150),
             stat_4 ~ px(150)) 
tbl1_gt

@@

plot_all_cytokines <- cytokines_long %>%
  filter(exp_number == "1") %>% 
  filter(tissue == sample_tissue) %>% 
  #filter(!variables %in% "INFg") %>%  #Exclude any cytokines not wanted in the plot
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  facet_wrap(~variables, 
             scales = 'free', 
             nrow = 5,
             ncol = 2) +
  labs(title = "Levels of pro-inflammatory cytokines in the ileum",  # Change title, and axis names
       x = "",
       y = "Tissue conc. (pg/mg)",
       fill = "Groups") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    #axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="white")) + # Change legend box background color
  scale_fill_brewer(palette="Set1")

@@

all_cytokines_patch <- plot_all_cytokines + plot_annotation (
  title = 'Cytokine expression',
   subtitle = 'All cytokines measured',
  tag_levels = 'A',
  caption = 'CON = Water, AB = Antibiotics, BF = Breast-Feeding, FF = Formula-Feeding',
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))

>>>>

```{r load data and set tissue type, include=FALSE}
#set tissue type
sample_tissue <- "ileum"
study_round <- "1"
```

@@

#Density plots to show distribution of cytokines
histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = values, fill = group)) + 
  geom_histogram() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

@@

tbl1 <- cytokines %>% 
  filter(exp_number == "1") %>% 
  filter(tissue == sample_tissue) %>% 
  select(group,INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  add_p() %>% 
  #modify_footnote("Exp. 1") %>% 
  modify_header(
    label ~ "**Groups:**")
  #modify_spanning_header((c("stat_1", "stat_2", "stat_3", "stat_4") ~ "Experiment 1 (N total = {N})")) %>%

  tbl1_gt <- tbl1 %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 20,
               heading.background.color = "lightgrey",
               ) %>% 
  tab_source_note(
    source_note = " *P-value indicates overall group differences"
  ) %>%
     tab_source_note(
    source_note = "Matrinem Experiment 1"
  ) %>%
  cols_width(label ~ px(200),
             stat_1 ~ px(150),
             stat_2 ~ px(200),
             stat_3 ~ px(200),
             stat_4 ~ px(200)) 
tbl1_gt

@@

plot_all_cytokines <- cytokines_long %>%
  filter(exp_number == "1") %>% 
  filter(tissue == sample_tissue) %>% 
  filter(!variables %in% c("INFg", "IL-12p70")) %>%  #Exclude any cytokines not wanted in the plot
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  facet_wrap(~variables, 
             scales = 'free', 
             nrow = 5,
             ncol = 2) +
  labs(title = "Levels of pro-inflammatory cytokines in serum",  # Change title, and axis names
       x = "",
       y = "Serum conc. (pg/ml)",
       fill = "Groups") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    #axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="white")) + # Change legend box background color
  scale_fill_brewer(palette="Set1")

@@

all_cytokines_patch <- plot_all_cytokines + plot_annotation (
  #title = 'Cytokine expression',
   #subtitle = 'All cytokines measured',
  #tag_levels = 'A',
  caption = 'CON = Water, AB = Antibiotics, BF = Breast-Feeding, FF = Formula-Feeding',
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))

### 2022-11-13 code/Round 2/FITC round 2.Rmd
Almost done with results

```{r load data and set tissue type, include=FALSE}
#set tissue type
study_round <- "2"

@@

fitc %>% 
  filter(exp_number == "2") %>% 
  drop_na(fitc_level) %>% 
  group_by(group) %>% 
  shapiro_test(fitc_level) 
#%>% filter(p < 0.05)

#Jitter plots. Works
jitter_plot <- fitc %>%
  filter(exp_number == 2) %>% 
  #filter(variables != "INFg") %>% 
  drop_na(fitc_level) %>% 
  ggplot(aes(x = group, y = fitc_level, color = group)) +
  geom_jitter()

no_outliers <- fitc %>% 
  filter(exp_number == 2) %>% 
  group_by(group2) %>% 
  mutate(fitc_level = ifelse(fitc_level > 10, mean(fitc_level), fitc_level))

>>>>

```{r load data and set tissue type, include=FALSE}
#set tissue type
study_round <- "4"

@@

fitc %>% 
  filter(exp_number == study_round) %>% 
  drop_na(fitc_level) %>% 
  group_by(group) %>% 
  shapiro_test(fitc_level) 
#%>% filter(p < 0.05)

#Jitter plots. Works
fitc %>%
  filter(exp_number == study_round) %>% 
  drop_na(fitc_level) %>% 
  ggplot(aes(x = group, y = fitc_level, color = group)) +
  geom_jitter()

no_outliers <- fitc %>% 
  filter(exp_number == study_round) %>% 
  group_by(group2) %>% 
  mutate(fitc_level = ifelse(fitc_level > 10, mean(fitc_level), fitc_level))

### 2022-11-13 code/Round 4/Cytokines round 4.Rmd
Almost done with results

```{r load data, echo=FALSE}
# Import dataset
#cytokines <- read_excel("../../Data/RawData/cytokines_round_1_r.xlsm")
cytokines <- read_excel("../../Data/CleanData/cytokines.xlsx")
glimpse(cytokines)
```

@@

Below is a table of the mean levels of cytokines in `r sample_tissue` tissue for each of the experimental groups.

The values will be displayed as mean + sd if normally distributed or median + IQR if not. An appropriate statistical test for differences will be performed (student-t for two, normally distributed groups, Anova for more than 2 groups, Kruskal wallis for non-normally distrubuted results.)

```{r}
tbl1 <- cytokines %>% 
  filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>% 
  select(group,INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no") %>%
  add_p() %>% 
  modify_header(
    label ~ "Cytokines",
    stat_1 = "**VANCO-BF (CON)**\n(n = {n})",
    stat_2 = "**VANCO-FF (FVT)**\n(n = {n})",
    stat_3 = "**VANCO-FF (SM)**\n(n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})"))

tbl1_gt <- tbl1 %>% 
 as_gt() %>%
  tab_header(title = md("**Proinflammatory cytokines (pg/mL)**")) %>%
  opt_align_table_header("center") %>% 
  tab_options(heading.title.font.size = 20,
              heading.background.color = "lightgrey",
              ) %>% 
  tab_source_note(
    source_note = " * P-value indicates overall group differences"
  ) %>%
  tab_source_note(
    source_note = md("**Matrinem round 4**")
  ) %>%
  cols_width(label ~ px(100),
             stat_1 ~ px(150),
             stat_2 ~ px(150),
             stat_3 ~ px(150)) 
tbl1_gt
# Save and export files
# tbl1 %>%  #Save as excel file.
#   as_hux_table() %>%
#   huxtable::quick_xlsx(., file = "../Results/Round 1/ileum-cytokines.xlsx")
# 
# tbl1 %>% #Save as image file.
# as_flex_table() %>%
#   flextable::save_as_image(path = "../../Results/Round 2/ileum_cytokines_table.png",webshot = "webshot")
```

>>>>

```{r load data, echo=FALSE}
# Import dataset
#cytokines <- read_excel("../../Data/RawData/cytokines_round_1_r.xlsm")
cytokines <- read_excel("data/processed/cytokines.xlsx")
glimpse(cytokines)
```

@@

```{r}
cytokines %>%   # run normality test on tissue weight
   filter(exp_number == 4) %>% 
  filter(tissue == sample_tissue) %>%
  group_by(type_of_feed) %>% 
  shapiro_test(tissue_weight_mg)

cytokines %>%       #Weight of tissue samples
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  geom_point() +

  labs(
    title = "Weight of intestinal samples",
      x = "",
       y = "Tissue weight (mg)",
       fill = "Groups",
       caption = "Matrinem round 4") +
  theme_bw()

```{r}
tbl1 <- cytokines %>% 
  filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>% 
  select(group,INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no") %>%
  add_p() %>% 
  modify_header(
    label ~ "Cytokines",
    stat_1 = "**VANCO-BF** \n(n = {n})",
    stat_2 = "**VANCO-FVF** \n(n = {n})",
    stat_3 = "**VANCO-SM** \n(n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})"))

tbl1_gt <- tbl1 %>% 
 as_gt() %>%
  tab_header(title = md("**Tissue conentration of proinflammatory cytokines** *(pg/mL)*")) %>%
  opt_align_table_header("center") %>% 
  tab_options(heading.title.font.size = 20,
              heading.background.color = "lightgrey",
              ) %>% 
  tab_source_note(
    source_note = md("**Matrinem round 4**")
  ) %>%
  cols_width(label ~ px(100),
             stat_1 ~ px(150),
             stat_2 ~ px(150),
             stat_3 ~ px(150)) 
tbl1_gt
# Save and export files
# tbl1 %>%  #Save as excel file.
#   as_hux_table() %>%
#   huxtable::quick_xlsx(., file = "../Results/Round 1/ileum-cytokines.xlsx")
# 
# tbl1 %>% #Save as image file.
# as_flex_table() %>%
#   flextable::save_as_image(path = "../../Results/Round 2/ileum_cytokines_table.png",webshot = "webshot")
```

### 2022-11-13 code/Round 4/FITC round 4.Rmd
Almost done with results

```{r load data, echo=FALSE}
# Import dataset
fitc <- read_excel("../../Data/CleanData/fitc.xlsx") %>% 
  rename(values = `result_µg/ml_undiluted`) %>% 
  drop_na(values)

@@

@@

normality_check <- fitc %>% 
  filter(exp_number == 4) %>% 
  group_by(group) %>% 
  shapiro_test(values)

normality_check %>% 
  filter(p < 0.05)

@@

```{r}
tbl1 <- fitc %>% 
  filter(exp_number == 4) %>% 
  mutate(Log10_values = log10(values)) %>% 
  select(group, values, Log10_values) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no",
              #type = list(values ~ 'continuous2', Log10_values ~ 'continuous2'),
              statistic = list(values ~ "{median} ({p25}, {p75})", Log10_values ~"{median} ({p25}, {p75})"),
              label = list(values ~ "µg/mL", Log10_values ~ "Log transformed")) %>%
  add_p(list(values ~ "kruskal.test", Log10_values ~ "kruskal.test")) %>% 
  # modify_table_styling(
  #   columns = label,
  #   rows = label == "µg/mL",
  #   footnote = "Non-parametric distribution"
  # ) %>% 
  modify_header(
    label = "FITC Conc.",
    stat_1 = "**VANCO-BF (CON)**\n(n = {n})",
    stat_2 = "**VANCO-FF (FVT)**\n(n = {n})",
    stat_3 = "**VANCO-FF (SM)**\n(n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})")) %>%  
  bold_labels()

tbl1_gt <- tbl1 %>% 
 as_gt(include = -tab_footnote) %>%
  tab_footnote( 
    footnote = md("Log transformation did not normalize distribution.  \n  Non-parametric test (Kruskall-Wallis) used for both datasets."),
    locations = cells_column_labels(columns = c(p.value))
  ) %>% 
  tab_header(title = md("**Intestinal permeability**")) %>%
  opt_align_table_header("center") %>% 
  tab_options(heading.title.font.size = 20,
              heading.background.color = "lightgrey"
              ) %>% 
  # tab_source_note(
  #   source_note = " µg/mL values"
  # ) %>%
  tab_source_note(
    source_note = md("**Matrinem round 4**")
  ) %>%
  cols_width(label ~ px(100),
             stat_1 ~ px(150),
             stat_2 ~ px(150),
             stat_3 ~ px(150))
tbl1_gt
# tbl1_gt %>% 
#   gtsave("../../Results/Round 4/FITC table round 3 TEST.png", expand = 50) #use .tex for latex files
```

This table can be exported with the following code either to word, excel, pdf, html or image files. See the syntax of huxtable and flextable (?flextable).

```{r ileum cytokine export, echo=TRUE, warning=FALSE}
tbl1_p <- tbl1 %>%
  filter_p() %>% 
  as_tibble()
```

@@

```{r long format, echo=FALSE}
fitc_long <- fitc %>% 
  filter(exp_number == 4)%>% 
  drop_na(
    values) %>% 
    mutate(Log10_values = log10(values)) %>% 
  mutate(
    group = recode_factor(#Change the order of the groups to desired plot order
      group,
      "CON-BF"= "VANCO-BF",
      "FVT-FORM" = "VANCO-FF (FVT)",
      "SM-FORM" = "VANCO-FF (SM)"
      ))

@@

Create a comparison vector to see pariwise comparisons.
```{r comparison list, warning=FALSE}
my_comparisons <- list(c("VANCO-BF", "VANCO-FF (FVT)"), c("VANCO-BF", "VANCO-FF (SM)"), c("VANCO-FF (FVT)", "VANCO-FF (SM)"))
```

Boxplots with jitter - normal values
```{r plots all fitc normal values, warning=FALSE}
plot_all_fitc <- fitc_long %>%
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  geom_point() +
  #coord_cartesian(ylim = c(1.5, 16)) + 
  stat_compare_means(comparisons = my_comparisons, label.y = c(60, 50, 45), method = "wilcox.test") +
  stat_compare_means(aes(label = paste0("Kruskal-Wallis \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.55) +
  labs( # Change title, and axis names
       x = "",
       y = "Serum FITC conc. (µg/ml)",
       fill = "Groups",
       caption = "Matrinem round 4") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    #axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"),#Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

all_fitc_patch <- plot_all_fitc + plot_annotation (
  title = 'Intestinal permeability',
   #subtitle = 'All fitc measured',
  #tag_levels = 'A',
  caption = 'VANCO = Vancomycin, BF = Breast-Feeding, FF = Formula-Feeding\n
  FVT = Fecal Virome Transfer, SM = SM-buffer',
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))

>>>>

```{r load data, echo=FALSE}
# Import dataset
fitc <- read_excel("data/processed/fitc.xlsx") %>% 
  rename(values = `result_µg/ml_undiluted`) %>% 
  drop_na(values)

@@

Set the tissue type and experimental round here:

```{r load data and set tissue type, include=FALSE}
#set tissue type
study_round <- "4"
```

@@

fitc %>% 
  filter(exp_number == study_round) %>% 
  group_by(group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

@@

```{r}
tbl1 <- fitc %>% 
  filter(exp_number == 4) %>% 
  #mutate(Log10_values = log10(values)) %>% 
  select(group, values) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,1,1),
              missing = "no",
              #type = list(values ~ 'continuous2', Log10_values ~ 'continuous2'),
              statistic = list(values ~ "{median} ({p25}, {p75})"),
              label = values ~ "µg/mL") %>%

  add_p() %>% 
  # modify_table_styling(
  #   columns = label,
  #   rows = label == "µg/mL",
  #   footnote = "Non-parametric distribution"
  # ) %>% 
  modify_header(
    label = "FITC Conc.",
    stat_1 = "**VANCO-BF** \n
    (n = {n})",
    stat_2 = "**VANCO-FVF** \n
    (n = {n})",
    stat_3 = "**VANCO-SM** \n
    (n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})")) %>%  
  bold_labels()

tbl1_gt <- tbl1 %>% 
 as_gt(include = -tab_footnote) %>%
  tab_footnote( 
    footnote = md("Median (IQR), Kruskal-Wallis."),
    locations = cells_column_labels(columns = c(p.value))
  ) %>% 
  tab_header(title = md("**Intestinal permeability**")) %>%
  opt_align_table_header("center") %>% 
  tab_options(heading.title.font.size = 20,
              heading.background.color = "lightgrey"
              ) %>% 
  # tab_source_note(
  #   source_note = " µg/mL values"
  # ) %>%
  tab_source_note(
    source_note = md("**Matrinem round 4**")
  ) %>%
  cols_width(label ~ px(100),
             stat_1 ~ px(150),
             stat_2 ~ px(150),
             stat_3 ~ px(150))
tbl1_gt
# tbl1_gt %>% 
#   gtsave("../../Results/Round 4/FITC table round 3 TEST.png", expand = 50) #use .tex for latex files
```

@@

```{r long format, echo=FALSE}
fitc_long <- fitc %>% 
  filter(exp_number == 4)%>% 
  drop_na(
    values) %>% 
    mutate(Log10_values = log10(values)) %>% 
  mutate(
    group = recode_factor(#Change the order of the groups to desired plot order
      group,
      "CON-BF"= "VANCO-BF",
      "FVT-FORM" = "VANCO-FVF",
      "SM-FORM" = "VANCO-SM"
      ))

@@

Create a comparison vector to see pariwise comparisons.
```{r comparison list, warning=FALSE}
my_comparisons <- list(c("VANCO-FVF", "VANCO-SM"), c("VANCO-BF", "VANCO-FVF"))
```

Boxplots with jitter - normal values
```{r plots all fitc normal values, warning=FALSE}
plot_all_fitc <- fitc_long %>%
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  geom_point() +
  coord_cartesian(ylim = c(10,35)) + 
  stat_compare_means(comparisons = my_comparisons, label.y = c(20, 25), method = "wilcox.test") +
  #stat_compare_means(aes(label = paste0("Kruskal-Wallis \n p = ", ..p.format..)),
   # label.y.npc = 0.75,
    #label.x.npc = 0.55) +
  labs( # Change title, and axis names
       x = "",
       y = "Serum FITC conc. (µg/ml)",
       fill = "Groups"
       #caption = "Matrinem round 4"
       ) +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    #axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"),#Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

all_fitc_patch <- plot_all_fitc + plot_annotation (
  title = 'Intestinal permeability',
   #subtitle = 'All fitc measured',
  #tag_levels = 'A',
  caption = 'FVF = Fecal Virome Filtrate, SM = SM-buffer  \n
  Pairwise comparisions using wilcoxon', 
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))
